Gravitational field calculation in spherical coordinates using variable densities in depth

### 2019-03-09 manuscript/manuscript.tex
Add more sinusoidal disclaimer in text
Add more sinusoidal disclaimer

We perform comparisons between the analytical solutions for the spherical shell and the
numerical integration results for linear, exponential, and sinusoidal density
functions.
The comparisons are repeated for all combinations of tesseroid models in
Table~\ref{tab:shell-models} and computation grids in Table~\ref{tab:grids}.
From these results, we generalize optimal values for $D$ and $\delta$ that ensure a
numerical error lower than 0.1\% of the spherical shell values for most use cases.

@@

So far we have tested the density-based discretization algorithm against linear and
exponential density functions.
Nevertheless, this new algorithm is well suited to more complex continuous functions,
for example non-monotonic functions or those with multiple inflection points.
Although such density functions are rarely, if ever, seen in geological structures,
we want to subject our algorithm to such cases in order to show that it can solve more
complex situations than linear and exponential functions.

>>>>

We perform comparisons between the analytical solutions for the spherical shell and the
numerical integration results for linear, exponential, and sinusoidal density
functions.
The sinusoidal density case is included in order to test the numerical approximation to
its limits.
The comparisons are repeated for all combinations of tesseroid models in
Table~\ref{tab:shell-models} and computation grids in Table~\ref{tab:grids}.
From these results, we generalize optimal values for $D$ and $\delta$ that ensure a
numerical error lower than 0.1\% of the spherical shell values for most use cases.

@@

So far we have tested the density-based discretization algorithm against linear and
exponential density functions.
Nevertheless, this new algorithm is well suited to more complex continuous functions,
for example non-monotonic functions or those with multiple inflection points.
Although such density functions are rarely, if ever, seen in geological structures,
we want to subject our algorithm to such cases in order to show that it can solve more
complex situations than linear and exponential functions.
Furthermore, acquiring an optimal value for the $\delta$ ratio in case of unrealistic
density functions allow to extrapolate it to simpler realistic cases.
Thus this tests are only intended to submit the algorithm to the extreme and not to
emulate a real case scenario.
